\chapter{Abstract} 
This project has primarily been focused on blood pressure measurement, where systolic- and diastolic values, as well as the pulse, could be determined. The purpose of this project is to construct hardware and software which can manipulate the pressure of an analog signal as well as depict this signal using developed software. By using an analog filter, the analog signal is amplified and sent to a Data Acquisition (DAQ), where the signal will be transformed from an analog signal to a digital signal. This digital signal will afterwards enter a computer, running the software program. Here the purpose of the software is to program an algorithm, which can detect a pulse as well as the systolic- and diastolic values. These two values are found by looking at the visualized signal.  From the beginning of the graph, and until the signal ascends to maximum. This max. value is the systolic value. Afterwards the signal will begin to descend until a minimum is reached, where this minimum is the diastolic value. The graph will then slightly climb again and begin a new period. From these systolic- and the diastolic values, the pulse can be found.\\
In addition to the above requirements, the program is able to be calibrated and zero adjusted, whenever the researcher finds it necessary. \\
This project is made for research use and it was therefore decided that a necessity for researcher, would be to save his measurements in a database. \\
The result of this project shows that it is possible to measure blood pressure through a combination of hardware and software. Through future development it could be possible for the program to detect hypertension (high blood pressure) and hypotension (low blood pressure). This would be useful if the project, in the future, would be used on patients. In this project however, the main goal has exclusively been measurements of blood pressure. 
